Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Adds discussion on the size of Q(R) and placeholders for other stuff

Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature. What we shall actually do is: introduce a finite group~$Q(G)$, and point out that 
\begin{itemize}
\item[(i)] it acts transitively on~(1), and simply transitively on (2)--(4);
\item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
\end{itemize}
The theorem follows immediately from these two observations, and from the following basic fact on group actions.

@@

@@

@@

\subsubsection*{On representations}

@@

\subsubsection*{On real nilpotent orbits}

@@

>>>>

Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature. What we shall actually do is: introduce a finite group~$Q(G)$, and point out that 
\begin{itemize}
\item[(i)] it acts transitively on~(1), and simply transitively on (2)--(4);
\item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
\end{itemize}

For the action on~(1) see Section~\ref{sec:action_DS}. For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}. For the action on~(4) and the equivariance of the map $\pi \mapsto \AV(\pi)$, see Section~\ref{sec:action_AV}. For the action on~(3) and the equivariance of $\pi \mapsto \WF(\pi)$ see Section~\ref{sec:action_WF}.

The theorem then follows immediately from observations (i)-(ii), and from the following basic fact on group actions, whose proof is left to the reader.

@@

\begin{remarkplain} \textup{The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group. It is trivial when $G$ is adjoint, and when $G$ is a simple group the cardinal of~$Q$ is at most~$4$. See Remark~\ref{rk:size_Q} for a more precise discussion.} \end{remarkplain}

\begin{remarkplain} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remarkplain}

@@

\begin{remarkplain} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.

In general, the group $G(\R)_{\ad}=(G^\sigma)_{\ad}$ contains the identity component of~$\Gad(\R)$, because the above injection $(G^\sigma)_{\ad} \hookrightarrow (\Gad)^\sigma$ is an isomorphism on the Lie algebra level. Therefore  $Q_\sigma(G)$ may be viewed as a quotient of the component group of $\Gad(\R)$, and is an elementary abelian $2$-group.

When $G(\R)$ is connected, which happens for instance if $G$ is simply connected, the group $G(\R)_{\ad}$ is itself connected, and therefore equal to the identity component of $\Gad(\R)$. In that case $Q_\sigma(\R)$ is isomorphic with the component group of $\Gad(\R)$.

For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}. In particular  $Q_\sigma(\R)$ has at most four elements in that case.
\end{remarkplain}

@@

\subsubsection{On representations} \label{sec:action_DS}

@@

\begin{center} \textcolor{red}{TO DO : explain that this preserves generic representations, and  DS representations within a single $L$-packet.\\ Then explain why the action is transitive.   }\end{center}

\subsubsection{\textcolor{red}{(NEW)} On Whittaker data}\label{sec:action_whitt}

\begin{center} \textcolor{red}{TO DO : explain how $Q_\sigma(G)$ acts on Whittaker data, and refer to \cite[Lemma 3.1.3]{adams_kaletha} for the simple transitivity; point out that $\pi \mapsto \Wh(\pi)$ is equivariant.   }\end{center}

\subsubsection{On real nilpotent orbits} \label{sec:action_WF}

@@

\subsubsection{On regular nilpotent $K$-orbits} \label{sec:action_AV}
